### 2018-06-28 Manuscript/carbonStabilizationMangrovesV2.tex
Addressed comments form reviewer 5

\subsection{Data analysis}
Comparison of group means for the different measured variables were performed using standard analysis-of-variance procedures. In all cases, we fitted a linear model between the response and the group variable (mangrove type) using the {\tt lm} function in the R language for statistical computing (The R Foundation, Vienna). Anova tables with summary statistics were obtained using the function {\tt anova} in R, including $F$-statistic, degrees of freedom, and $p$-values. Data and code to reproduce all results presented here can be obtained from the following repository \url{https://github.com/crlsierra/mangroveCstabilization.git}.

@@

We found important differences between fringe and basin mangroves in terms of \%OC ($p$-value $< 0.001$; analysis of variance $F$-test, $F = 54.13$ with 49 degrees of freedom) and \%TN ($p$-value $< 0.001$, $F = 27.1$ with 49 d.f.) (Fig. \ref{fig:2}). In general, \%OC and \%TN decreased with soil depth, with a more clear trend for \%OC than \%TN.

@@

Differences in bulk densities between the two forest types resulted in a completely different distribution of C compared to the previous results based on \%OC alone (Table \ref{tab:1}). A higher carbon storage in the upper layers of basin mangrove soils is clearly outlined (Table \ref{tab:1}). The differences in TOC between basin and fringe mangrove types are significant according to the one-way analysis of variance test ($p$-value $= 0.032$, $F = 4.88$, 48 d.f.). TOC decreased with soil depth within the first four (basin) and three (fringe) layers. There was an increase in TOC for the last measured depth intervals of basin and fringe soils, which can be traced back to higher \%OC values of those layers.

>>>>

\subsection{Data analysis}
We performed statistical tests to determine differences in organic carbon concentrations, total nitrogen, $\delta^{13}$C, Fe- and Al-oxides, among the fringe and basin mangroves. After an initial test for normality (Shapiro-Wilk test), we found little evidence to support the normality assumption required in common tools such as ANOVA or t-tests. We therefore, performed the non-parametric Mann-Whitney U test, which is equivalent to the two-sample Wilcoxon test \citep{Hollander2015} under the null hypothesis that the samples from the fringe and basin mangroves  differ by a shift location $\mu =0$, and the alternative hypothesis that they different by some other shift location. In other words, the test helps to determine whether the samples from the two different mangrove types belong to the same statistical distribution as stated in the null hypothesis. Data and code to reproduce all results presented here can be obtained from the following repository \url{https://github.com/crlsierra/mangroveCstabilization.git}.

%Comparison of group means for the different measured variables were performed using standard analysis-of-variance procedures. In all cases, we fitted a linear model between the response and the group variable (mangrove type) using the {\tt lm} function in the R language for statistical computing (The R Foundation, Vienna). Anova tables with summary statistics were obtained using the function {\tt anova} in R, including $F$-statistic, degrees of freedom, and $p$-values. Data and code to reproduce all results presented here can be obtained from the following repository \url{https://github.com/crlsierra/mangroveCstabilization.git}.

@@

We found important differences between fringe and basin mangroves in terms of \%OC ($p$-value $< 0.001$; two-sample Wilcoxon $W$-test, $W = 62$) and \%TN ($p$-value $< 0.001$, $W = 102$) (Fig. \ref{fig:2}). In general, \%OC and \%TN decreased with soil depth, with a more clear trend for \%OC than \%TN.

@@

Differences in bulk densities between the two forest types, multiplied by \% organic carbon, resulted in a completely different distribution of C compared to the previous results based on \%OC alone (Table \ref{tab:1}). A higher carbon storage in the upper layers of basin mangrove soils is clearly outlined (Table \ref{tab:1}). Summed across the profile, fringe mangroves had a TOC of 387.77 $\pm$ 125.77 Mg C ha$^{-1}$, and basing mangroves an average TOC of 665.41 $\pm$ 434.65 Mg C ha$^{-1}$. Given this large variability, we did not find enough evidence to reject the hypothesis that TOC from these two forest types are sampled from the same distribution  ($p$-value $= 0.47$, $W = 350$). TOC decreased with soil depth within the first four (basin) and three (fringe) layers. There was an increase in TOC for the last measured depth intervals of basin and fringe soils, which can be traced back to higher \%OC values of those layers.

### 2018-06-28 Reviews/Response2.tex
Addressed comments form reviewer 5

>>>>

{\color{blue} Thanks for pointing this our. We originally applied an ANOVA test without checking the normality assumption. After checking for normality using the Shapiro-Wilk test, we found that the normally assumption was not met by our data, even after trying different transformations. Therefore, we decided to apply a non-parametric test, the Mann-Whitney U test to determine whether the two independent samples from the fringe and basin mangroves are from the same distributions. After running this test for all the measured variables, we found the same results as with the initial comparison using ANOVA. Therefore, our conclusions are unchanged despite applying a different statistical test. }
